%-------------------------
% Resume in Latex
% Author : Srivatsav N.D.
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\setlength{\footskip}{4.08003pt}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[dvipsnames]{xcolor}
\input{glyphtounicode}

% Using FiraSans
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}



%----------FONT OPTIONS----------
% sans-serif
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace {-10pt}\color{Blue}\raggedright\large\bfseries
}{}{0em}{}[\color{Blue}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\workexp}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge\bfseries \MakeUppercase{SRIVATSAV N.D.}}\\[1pt]
    \small
    \raisebox{-0.1\height}\faPhone~+91 9943171536 ~|~ 
    \raisebox{-0.2\height}\faEnvelope~\href{mailto:srivatsavsurya11@gmail.com}{srivatsavsurya11@gmail.com} ~|~ 
    \raisebox{-0.2\height}\faLinkedin~\href{https://www.linkedin.com/in/srivatsav-n-d/}{srivatsav n.d.} ~|~ 
    \raisebox{-0.2\height}\faGithub~\href{https://github.com/srivatsavsurya}{srivatsavsurya}
\end{center}
\vspace{-8pt}

%-----------EDUCATION-----------
\section*{EDUCATION}
\resumeSubHeadingListStart

  \resumeSubheading
    {Thiagarajar College of Engineering}{Madurai, Tamil Nadu}
    {B.E. in Mechatronics Engineering \textbar{} CGPA: 8.39/10}{2020 -- 2024}

  \resumeSubheading
    {buildspace}{Remote}
    {Project-based 6-week Program}{2023 -- 2024}

\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section*{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart

  \workexp
    {Software Development Engineer | alfaTKG}{Jun 2024 -- Present}
    {}{}
    \resumeItemListStart
      \resumeItem{Developed AI-powered chatbot and scheduling systems, automating 70\% of customer queries.}
      \resumeItem{Delivered a full-stack software suite for sheet metal manufacturing with real-time monitoring and analytics.}
    \resumeItemListEnd

  \workexp
    {Robotic Simulation Engineer Intern | alfaTKG}{Dec 2022 -- Aug 2023}
    {}{}
    \resumeItemListStart
      \resumeItem{Generated high-precision robotic simulations using RoboDK for Yaskawa robots, improving deployment accuracy.}
      \resumeItem{Automated robot programming workflows, cutting process time by 60\%.}
    \resumeItemListEnd

  \workexp
    {Open Source Developer | Timechain Labs}{May 2023 -- Jul 2023}
    {}{}
    \resumeItemListStart
      \resumeItem{Integrated Bitcoin Lightning Network backend for processing 10K+ micropayments daily.}
      \resumeItem{Designed "Add to Wallet" UI/UX for neucron.io, increasing engagement by 40\%.}
    \resumeItemListEnd

  \workexp
    {Mechanical Design Engineer | Team Eureka}{Jun 2021 -- Nov 2022}
    {}{}
    \resumeItemListStart
    \resumeItem{Contributed to a cross-functional team that won SAE-ISS 2022, supporting the management of a Rs.50K budget and advancing FEA for optimized bicycle frame design.}    \resumeItemListEnd
    \vspace{3pt}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section*{TECHNICAL PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{IntelliDrip} | \emph{IoT, Arduino, ESP32, Cloud Integration} | SIH (Cyient): SK2}
  {\href{https://github.com/srivatsavsurya/intelliDrip}{\faGithub}}
  \resumeItemListStart
    \resumeItem{Built an IoT-based IV monitor with real-time alerts and predictive analytics, reducing attention time by 65\%.}
    \resumeItem{Designed a modular, low-cost device compatible with 90\% of IV stands.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{AutoDrive} | \emph{Python, Computer Vision, ADAS, CARLA, CAN, \href{https://comma.ai/openpilot}{openpilot}}}
  {\href{https://github.com/srivatsavsurya/AutoDrive}{\faGithub}}
\resumeItemListStart
  \resumeItem{Initiated development of a Level 2 autonomous driving stack targeting 95\%+ lane detection accuracy using CARLA simulator and CNN-based perception.}
  \resumeItem{Designed real-time object detection and CAN-based vehicle control framework inspired by openpilot architecture.}
\resumeItemListEnd

  \resumeProjectHeading
  {\textbf{Pothole Detection \& Reporting System} | \emph{IoT,  Raspberry Pi, ESP32, Cloud} | SIH (DRDO): NR1177}
  {\href{https://github.com/srivatsavsurya/pothole-detection}{\faGithub}}
  \resumeItemListStart
    \resumeItem{Created ML model for pothole detection with 92\% accuracy using edge video feeds.}
    \resumeItem{Developed scalable cloud backend with mobile reporting app for municipalities.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section*{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=-1pt, label={}]
    \small{\item{
     \textbf{Programming}{: Python (OpenCV, TensorFlow, PyTorch, NumPy, Pandas), C/C++, JavaScript/TypeScript, HTML/CSS, SQL} \vspace{1pt}\\
     \textbf{Technologies}{: Git, Linux, Docker, Arduino, Raspberry Pi, NodeMCU} \vspace{1pt}\\
     \textbf{Design}{: SOLIDWORKS, Fusion360, EasyEDA, RoboDK} \vspace{1pt}\\
     \textbf{Industrial}{: Bosch Rexroth PLC, Yaskawa Robots, MATLAB/Simulink, AI \& Machine Learning, Digital Twin, Industry 4.0}
    }}
 \end{itemize}
 
%-----------ACHIEVEMENTS-----------
\section*{AWARDS \& ACHIEVEMENTS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tamil Nadu Student Innovators (TNSI)}{2022}
      {Selected among top 3 from 13,300+ applicants}{EDII-TN}
      \resumeItemListStart
        \resumeItem{Secured Rs.1 lakh funding and 6-month mentorship program for IntelliDrip project, leading to successful prototype development and clinical trials in 2 hospitals.}
        \resumeItem{Featured in Tamil Nadu Innovation Hub and recognized by State MSME Minister for developing cost-effective healthcare solutions.}
      \resumeItemListEnd
    \vspace{1pt}
    
    \resumeSubheading
      {SAE-ISS Bicycle Design Competition}{2022}
      {Overall Championship}{National Level}
      \resumeItemListStart
        \resumeItem{Secured first place among 45+ teams nationwide, winning as Overall Performance Bicycle.}
      \resumeItemListEnd
    \vspace{1pt}
    
    \resumeSubheading
      {Technical Achievements}{2020-2024}
      {Various Competitions \& Certifications}{}
      \resumeItemListStart
        \resumeItem{Achieved 1st place in National IoT Quiz Challenge among 500+ participants, hosted by AICTE in collaboration with AWS and Intel.} 
        \resumeItem{Top 5 finalist in SIH 2023 (Hardware Edition) – Problem SIH1375 by Ministry of Power;  informally recognized as runner-up by jury.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
 